\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.45in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\pagestyle{empty}

\titlespacing*{\section}{0pt}{4pt}{2pt}
\titleformat{\section}{\bfseries\small}{}{0em}{}[\titlerule]

\setlist[itemize]{leftmargin=*,nosep}

\begin{document}

\begin{center}
{\Large \textbf{Nayanpriya}}\\
Jaipur, Rajasthan $\vert$ +91-9321624088 $\vert$ nayan.priya2308@gmail.com\\
LinkedIn $\vert$ GitHub $\vert$ LeetCode
\end{center}

\section*{SUMMARY}
Computer Science Engineering student with strong foundations in Python, SQL, Data Structures, Algorithms, Data Analytics, and Machine Learning. Experienced in building AI-powered applications, analytics platforms, and business intelligence solutions. Passionate about solving business problems using data, programming, and modern AI technologies.

\section*{EDUCATION}
\textbf{Manipal University Jaipur} \hfill 2023--2027\\
B.Tech, Computer Science and Engineering \hfill CGPA: 8.16

\section*{EXPERIENCE}
\textbf{Trainee Intern, Edunet Foundation} \hfill Dec 2024 -- Jan 2025
\begin{itemize}
\item Developed Power BI dashboards for energy consumption analysis and reporting.
\item Performed data cleaning, transformation, aggregation, and DAX-based calculations.
\item Generated actionable insights through KPI reporting and trend analysis.
\end{itemize}

\section*{PROJECTS}

\textbf{AI Data Query \& Visualization Platform} \hfill 2026\\
{\footnotesize Node.js, React.js, Next.js, PostgreSQL, Recharts}
\begin{itemize}
\item Built a full-stack analytics platform for ingesting CSV datasets and storing structured data for analysis.
\item Developed APIs for data extraction, transformation, validation, analytics generation, and SQL-based querying.
\item Implemented conversational dataset querying and interactive dashboards for KPI tracking and trend analysis.
\end{itemize}

\textbf{AI Code Reviewer \& MCP Server} \hfill 2026\\
{\footnotesize Java, LangChain4j, Apache Maven, PMD}
\begin{itemize}
\item Built a Java-based AI code review server using LangChain4j and Gemini API.
\item Integrated PMD static analysis with secure sandboxed execution and automated code explanations.
\end{itemize}

\textbf{Energy Consumption Trend Analysis} \hfill 2025\\
{\footnotesize Power BI, Excel}
\begin{itemize}
\item Built dashboards to analyze energy usage trends across regions and sectors.
\item Performed data cleaning and DAX calculations to generate business insights.
\end{itemize}

\section*{TECHNICAL SKILLS}
\textbf{Languages:} Python, Java, SQL, C++\\
\textbf{Data Analytics \& Engineering:} Data Cleaning, Data Transformation, Data Visualization, ETL Fundamentals, Power BI, KPI Reporting\\
\textbf{Databases:} PostgreSQL, SQLite, SQL Querying\\
\textbf{AI/ML:} PyTorch, Scikit-Learn, Transformers, Prompt Engineering, LangChain4j\\
\textbf{Tools:} Git, GitHub, Maven, Jupyter Notebook, VS Code

\section*{CERTIFICATIONS}
Supervised Machine Learning (Coursera) $\vert$
Advanced Learning Algorithms (Coursera) $\vert$
C++ (Scaler) $\vert$
Object Oriented Design in Java (GeeksforGeeks)

\end{document}
